Handling missing data in smartphone location logs

### 2018-04-29 report/thesisReportApa.tex
APA manuscript

  \def\affdep{{""}}%
  \def\affcity{{""}}%

@@

  \authornote{
    \newcounter{author}
    Department of Methodology \& Statistics

@@

                      Correspondence concerning this article should be addressed to Boaz Sobrado. E-mail: \href{mailto:boaz@boazsobrado.com}{\nolinkurl{boaz@boazsobrado.com}}
                }

@@

\usepackage{amsthm}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\theoremstyle{definition}
\newtheorem{example}{Example}
\theoremstyle{definition}
\newtheorem{exercise}{Exercise}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\begin{document}

>>>>

  % \def\affdep{{""}}%
  % \def\affcity{{""}}%

@@

  \authornote{
    Department of Methodology \& Statistics

@@

    Correspondence concerning this article should be addressed to Boaz
    Sobrado, . E-mail:
    \href{mailto:boaz@boazsobrado.com}{\nolinkurl{boaz@boazsobrado.com}}
  }

@@

\usepackage{amsthm}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{definition}
\newtheorem{exercise}{Exercise}[section]
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\begin{document}
